WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-12 paper/ms.tex
add updated method section

Using the cleaned PDC lightcurve, we ran Box Least Squares (BLS) to
estimate the transit epoch, period, and duration
\citep{kovacs_box-fitting_2002}.  Using these parameters, we isolated
each transit to within $\pm$5 transit durations of its midtime.  In
each transit window, we then simultaneously fit for a model transit,
plus a local linear trend.  Our transit model uses the analytic
formulae calculated by \citet{mandel_analytic_2002} and implemented by
\citet{kreidberg_batman_2015}.

We allowed four free parameters per transit: the time of mid-transit
$t_{\rm tra}$, the planet-to-star radius ratio $R_{\rm p}/R_\star$,
and the slope and intercept of the line.
% Our priors were wide uniform distributions centered on the BLS
% estimates for $t_{\rm tra}$ and $R_{\rm p}/R_\star$, and on a slope
% of zero and an intercept of unity for the line.
We fixed the remaining transit parameters as follows.  We set the
eccentricity to zero. We
assumed a quadratic limb-darkening law, with coefficients interpolated
from the \citet{claret_limb_2017} tables.  For the period,
$a/R_\star$, and inclination, we adopted the values
from~\citet{petrucci_no_2013}.  These are in reasonable agreement with
the parameters reported by \citet{gillon_improved_2009},
\citet{southworth_high-precision_2009}, and
\citet{huitson_gemini_2017}.

Having defined the free and fixed parameters, we calculated an initial
guess for the free parameters by maximizing the likelihood.  We then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
% During this process, we used the \texttt{corner} software to check
% that our posteriors were being well-sampled~\citep{corner_2016}.
After completing an initial fit, we set the photometric error bars to
be equal to the standard deviation of the out-of-transit points of the
residual lightcurve.  We then reperformed the fitting procedure, using
the empirically determined photometric errors.

@@

Figure~\ref{fig:lightcurves} shows the light curves, best-fit models,
and residuals.  Table~1 reports the mid-transit times and their
uncertainties.  Taking the mean and standard deviation of the measured
planet to star radius ratio, we find $R_{\rm
p}/R_\star=0.1538\pm0.0013$, in agreement with previous determinations
\citep{wilson_wasp-4b_2008,gillon_improved_2009,winn_transit_2009,southworth_high-precision_2009}.
Binning the residuals to 1-hour windows and taking the median absolute
deviation, the lightcurves have an RMS of $586\,{\rm ppm}\,{\rm
hr}^{1/2}$.  The predicted\footnote{\url{github.com/lgbouma/tnm}}
photon-counting noise is $410\,{\rm ppm}\,{\rm hr}^{1/2}$.  At
$T\approx11.8$, with a 9-pixel aperture read noise is expected to
contribute an additional $202\,{\rm ppm}\,{\rm hr}^{1/2}$ in
quadrature.  The predicted zodiacal background contribution is
$673\,{\rm ppm}\,{\rm hr}^{1/2}$, based on the
\citet{winn_photonflux_2013} model, which \citet{Sullivan_2015} used
in planet detection simulations.  This zodiacal noise prediction seems
to have been an overestimate, given the observed RMS of WASP-4.  A
more detailed assessment of TESS's photometric performance is beyond
the scope of this work.

@@

\begin{deluxetable}{lccc}
\tabletypesize{\scriptsize}
\tablecaption{Selected system parameters of WASP-4b\label{tbl:params}}
\tablenum{2}

\tablehead{
\colhead{Parameter} & \colhead{Value} & \colhead{Error} & \colhead{Comment}
}

\startdata
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.1538$               & $\pm 0.0013$                & A \\
  $i$~[deg]                                  & $88.52$                & $+0.39$, $-0.26$            & B \\
  $a/R_\star$                                & $5.463$                & $+0.025$, $-0.020$          & B \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & C \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & D \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & D \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & D \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & E \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & G \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & F \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.722$                & $+0.024$, $-0.019$          & A \\
  $M_\star$~[M$_{\odot}$]                    & $0.870$                & $+0.085$, $-0.077$          & F \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & H \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0007$                & F \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.192$                & $+0.091$, $-0.086$          & F \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.337$                & $\pm 0.048$                 & F \\
\enddata

\tablecomments{
  (A) From TESS lightcurves (\S~\ref{sec:measurement}).
  (B) \citet{hoyer_tramos_2013}.
  (C) \citet{triaud_spin-orbit_2010}.
  (D) From HARPS spectra \citep{doyle_accurate_2013}.
  (E) \citet{stassun_accurate_2017}.
  (F) From functions of stellar, transit or RV parameters as discussed in text.
  (G) {\it Gaia} DR2.
  (H) \citet{stassun_TIC_2018}.
}

>>>>

Using the cleaned PDC lightcurve, we ran Box Least Squares (BLS) to
determine the orbital period, and to estimate the transit duration and
a reference epoch \citep{kovacs_box-fitting_2002}.  From these
parameters, we isolated each transit to within $\pm$4 transit
durations of its midtime.  We then fit the phase-folded transit, using
the analytic formulae calculated by \citet{mandel_analytic_2002} and
implemented by \citet{kreidberg_batman_2015}.  Specifically, we fit
for a reference epoch, the planet to star radius ratio $R_{\rm
p}/R_\star$, the semi-major axis to stellar radius ratio $a/R_\star$,
the inclination $i$, two quadratic limb-darkening coefficients
$(u_{\rm linear}, u_{\rm quad})$, and the orbital period $P$.  We set
the eccentricity to zero.

Having defined the free and fixed parameters, we calculated an initial
guess for the free parameters by maximizing the likelihood.  We then
sampled over the posterior using the algorithm proposed by
\citet{goodman_ensemble_2010} and implemented by
\citet{foreman-mackey_emcee_2013}.
Table~1 gives the results, which are in reasonable agreement with the
parameters reported by \citet{gillon_improved_2009},
\citet{southworth_high-precision_2009}, and
\citet{huitson_gemini_2017}.
%TODO: is this true? Or do the periods actually differ?

To measure mid-transit times, we then focused on each individual
transit window.  We fit for a model transit, plus a local linear
trend.  We allowed four free parameters per transit: the time of
mid-transit $t_{\rm tra}$, the planet-to-star radius ratio $R_{\rm
p}/R_\star$, and the slope and intercept of the line.  We fixed the
remaining parameters~--~$a/R_\star$, $i$, $P$, and the limb-darkening
coefficients~--~to the best-fit values from the global fit.

% During this process, we used the \texttt{corner} software to check
% that our posteriors were being well-sampled~\citep{corner_2016}.
After completing an initial fit for each transit, we set the
photometric error bars to be equal to the standard deviation of the
out-of-transit points of the residual lightcurve.  We then reperformed
the fitting procedure, using the empirically determined photometric
errors.

@@

Figure~\ref{fig:lightcurves} shows the light curves, best-fit models,
and residuals.  Table~2 reports the mid-transit times and their
uncertainties.
Binning the residuals to 1-hour windows and taking the median absolute
deviation, the lightcurves have an RMS of $586\,{\rm ppm}\,{\rm
hr}^{1/2}$.  The predicted\footnote{\url{github.com/lgbouma/tnm}}
photon-counting noise is $410\,{\rm ppm}\,{\rm hr}^{1/2}$.  At
$T\approx11.8$, with a 9-pixel aperture read noise is expected to
contribute an additional $202\,{\rm ppm}\,{\rm hr}^{1/2}$ in
quadrature.  The predicted zodiacal background contribution is
$673\,{\rm ppm}\,{\rm hr}^{1/2}$, based on the
\citet{winn_photonflux_2013} model, which \citet{Sullivan_2015} used
in planet detection simulations.  This zodiacal noise prediction seems
to have been an overestimate, given the observed RMS of WASP-4.  A
more detailed assessment of TESS's photometric performance is beyond
the scope of this work.

@@

\begin{deluxetable}{lccc}
\tabletypesize{\scriptsize}
\tablecaption{Selected system parameters of WASP-4b\label{tbl:params}}
\tablenum{1}

\tablehead{
\colhead{Parameter} & \colhead{Value} & \colhead{Uncertainty} & \colhead{Comment}
}

\startdata
%FIXME with new method
%TODO numbers with updated method
{\it Transit/RV parameters:} & & & \\
  $R_{\rm p}/R_\star$                        & $0.1538$               & $\pm 0.0013$                & A \\
  $i$~[deg]                                  & $88.52$                & $+0.39$, $-0.26$            & A \\
  $a/R_\star$                                & $5.463$                & $+0.025$, $-0.020$          & A \\
  $u_{\rm linear}$                           & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $u_{\rm quad}$                             & $0.XXX$                & $+0.XXX$, $-0.XXX$          & A \\
  $K$~[m~s$^{-1}$]                           & $241.1$                & $+2.8$, $-3.1$              & B \\
{\it Stellar parameters:} & & & \\
  $T_{\rm eff}$~[K]                          & $5400$                 & $\pm 90$                    & C \\
  $\log g_\star$~[cgs]                       & $4.47$                 & $\pm 0.11$                  & C \\
  $[{\rm Fe/H}]$                             & $-0.07$                & $\pm 0.19$                  & C \\
  $F_{\rm bol}$~[erg~cm$^{-2}$~s$^{-1}$]     & $2.802\times10^{-10}$  & $\pm 0.076\times10^{-10}$   & D \\
  $\pi$~[mas]                                & $3.7145$               & $0.0517$                    & F \\
  $R_\star$~[R$_{\odot}$]                    & $0.893$                & $\pm 0.034$                 & E \\
  $\rho_\star$~[g~cm$^{-3}$]                 & $1.722$                & $+0.024$, $-0.019$          & E \\
  $M_\star$~[M$_{\odot}$]                    & $0.870$                & $+0.085$, $-0.077$          & E \\
  $T$ magnitude                              & $11.778$               & $\pm 0.018$                 & G \\
{\it Planetary parameters:} & & & \\
  $a$~[AU]                                   & $0.0227$               & $\pm 0.0007$                & E \\
  $M_p$~[M$_{\rm Jup}$]                      & $1.192$                & $+0.091$, $-0.086$          & E \\
  $R_p$~[R$_{\rm Jup}$]                      & $1.337$                & $\pm 0.048$                 & E \\
\enddata

\tablecomments{
  (A) From TESS lightcurves (\S~\ref{sec:measurement}). Orbital periods from timing data are in Table~4.
  (B) \citep{triaud_spin-orbit_2010}.
  (C) From HARPS spectra \citep{doyle_accurate_2013}.
  (D) \citet{stassun_accurate_2017}.
  (E) From functions of stellar, transit or RV parameters as discussed in text.
  (F) {\it Gaia} DR2.
  (G) \citet{stassun_TIC_2018}.
}
